Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-15 Administratie/report/paper.tex
update

Eroding is a morphology operator to make the objects on the foreground, which are the brightest, smaller \cite{sreedhar2012enhancement}. Figure \ref{line_zoom_eroded} shows an example of a thinned white line. When the kernel is large enough, white lines can be filtered out completely. The same technique is used to smooth the surface of cobbled roads. A cobblestone consist of a bright center, surrounded by darker joints. By eroding the cobbled road, the erode function will minimize the center of the cobble, which will cause enlarged joints. With a large kernel, the joints will spread until they overlap. The best results were achieved with an ellipsoidal kernel of 100 x 30 px.

@@

The combination of road classification and edge detection starts with removing outliers from the road classification. The goal of this is to eliminate the effect an outlier would have when it's close to the car. A non-road block is considered an outlier when it has less than 4 non-road block neighbours. This is repeated until we become a stable condition without outliers.

@@

When the edge is not classified on the road, it is added to a collection. The intersections of the edges in the collection and the masks are computed. For each frame the masks give the projected trajectory of the car. 
The edges are visualised as blue lines on figure \ref{zebra}. The intersections are shown green. The closest intersection to the car is shown in red. At this point the maximum speed is derived from the intensity.

@@

An other way to make a combination, witch still results in zero crashes is to focus on edge detection. A region is considered road if there are no edges. When there are edges, road classification is used to decide whether it's road. This strategy gave us the best results and are shown as the fourth bar.
\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{fig/distance_result.png}
	\caption{Results of road classification, edge detection and combinations.\label{distance_result}}
\end{figure}

>>>>

Eroding is a morphology operator to make the objects on the foreground, which are the brightest, smaller \cite{erode_dilate}. Figure \ref{line_zoom_eroded} shows an example of a thinned white line. When the kernel is large enough, white lines can be filtered out completely. The same technique is used to smooth the surface of cobbled roads. A cobblestone consist of a bright center, surrounded by darker joints. By eroding the cobbled road, the erode function will minimize the center of the cobble, which will cause enlarged joints. With a large kernel, the joints will spread until they overlap. The best results were achieved with an ellipsoidal kernel of 100 x 30 px.

@@

In order to combine road classification and edge detection two methods were tested:
\begin{enumerate}
\item  A region is considered road only if it's identified as road by the road classification and there are no edges. 
\item A region is considered road if there are no edges. When there are edges, road classification is used to decide whether it's road. 
\end{enumerate}

The combination of road classification and edge detection starts with removing outliers from the road classification. The goal of this is to eliminate the effect an outlier would have when it's close to the car. A non-road block is considered an outlier when it has less than 4 non-road block neighbours. This is repeated until all outliers are removed.

@@

When the edge is not classified as road, it is added to a collection. The intersections of the edges in the collection and the masks are computed. For each frame the masks give the projected trajectory of the car. 
The edges are visualised as blue lines on figure \ref{visualization}. The intersections are shown green. The closest intersection to the car is shown in red. At this point the maximum speed is derived from the intensity.

\begin{figure}[t]
  \centering
  \includegraphics[width=.9\textwidth]{fig/frame00025.png}
  \caption{Visualization of a processed frame showing both classification and edge detection}
  \label{visualization}
\end{figure}

@@

An other way to make a combination, which still results in zero crashes is to focus on edge detection. A region is considered road if there are no edges. When there are edges, road classification is used to decide whether it's road. This strategy gave us the best results and are shown as the fourth bar.
\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth]{fig/distance_result.png}
	\caption{Results of road classification, edge detection and combinations.\label{distance_result}}
\end{figure}
